---
title: "News"
output:
  html_document:
    include:
      before_body: 4_news_topbar.html
      after_body: footer.html
    css: 4_news_style.css
---

*2018-03-09* **[Amazing Pictures from the GlobE-wetlands project
](https://photos.google.com/share/AF1QipOkR46_z-5CmhLalP3ckv_rck3-4sCYDz4NNWSGgTDdY1K4e7-wH9MCGUSfAgUSuQ?key=eklJUmhFT05ORHdUdVFHUzJhcVE2R3BwTEI5YUxn)**

*2018-01-06* **[Floogin in Troisdorf-Bergheim,
Germany](https://photos.google.com/share/AF1QipPr8y7V3CbaYCzMXPqQYagYBBMNjbxy3bF8--ZYM7LyhYJ41Ul8LwTjdJrZaZ8NTA?key=c3NNTWxKaHB5S2hCZHBHVXdjbVFHc1hDTDktdjdR)**

<br/>

Old Posts (to be edited!)

<br/>

<div style="background-color: #d2d3dc; text-align: left; padding: 10px;
border-radius: 15px">

# Package vegtable is on CRAN
*2017-08-08*

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/vegtable)](https://cran.r-project.org/package=vegtable)
[![total downloads](http://cranlogs.r-pkg.org/badges/grand-total/vegtable)](http://cranlogs.r-pkg.org/badges/grand-total/vegtable)

The package `vegtable` defines an object containing vegetation-plot data
sets and many functions for handling these data.
You can install it in your **R** session:

```{r install_vegtable_cran, eval=FALSE}
install.packages("vegtable", dependencies=TRUE)
```

To load the last version from **GitHub** you can still use:

```{r install_vegtable_github, eval=FALSE}
library(devtools)
install_github("kamapu/vegtable", build_vignettes=TRUE)
```

Examples of its applications are available at
[https://kamapu.github.io/documents/workshops_freiburg_2017.html](https://kamapu.github.io/documents/workshops_freiburg_2017.html).

</div>


<br/>

<div style="background-color: #deefbc; text-align: left; padding: 10px;
border-radius: 15px">

# Package taxlist launched in CRAN
*2017-06-14*

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/taxlist)](https://cran.r-project.org/package=taxlist)
[![total downloads](http://cranlogs.r-pkg.org/badges/grand-total/taxlist)](http://cranlogs.r-pkg.org/badges/grand-total/taxlist)

After a long time of conceptualization and development, `taxlist` is already
available at **CRAN**.
Thus you can install it in your **R** session:

```{r install_cran, eval=FALSE}
install.packages("taxlist", dependencies=TRUE)
```

To load the last version from **GitHub** you can still use:

```{r install_github, eval=FALSE}
library(devtools)
install_github("kamapu/taxlist", build_vignettes=TRUE)
```

Examples of its use will be published in
[Workshops](https://kamapu.github.io/workshops.html)

</div>

<br/>
