---
title: "sudamerica"
output:
  html_document:
    include:
      before_body: topnfoot/sudamerica_topbar.html
      after_body: topnfoot/footer.html
    css: css/databases_style.css
---

**A database for vegetation-plots in South America**

[![GIVD](badges/sudamerica_givd.svg)](http://www.givd.info/ID/SA-CL-001)
[![version](badges/sudamerica_version.svg)](sudamerica.html)


```{r import_sudamerica, echo=FALSE, results="hide"}
load("M:/WorkspaceR/00_Documents/update_databases/sudamerica.rda")
```

The database **sudamerica** is formatted in **PostgreSQL**, including the
extension **PostGIS**.
For data exchange (after a respective agreement with the custodian), objects of
class [**`vegtable`**](https://github.com/kamapu/vegtable) will be preferred.

**sudamerica** contains currently records from
**`r format(nrow(sudamerica_table), big.mark=",")`** plot observations that are
provided by
**`r format(length(unique(sudamerica_table$data_source)), big.mark=",")`**
sources.
Most of those sources are works published either as journal articles or
monographs.

The oldest record was done in
**`r format(min(sudamerica_table$record_date, na.rm=TRUE), "%d-%m-%Y")`**,
while the newest record is from
**`r format(max(sudamerica_table$record_date, na.rm=TRUE), "%d-%m-%Y")`**.

```{r map_sudamerica, echo=FALSE, message=FALSE, out.width="100%"}
library(leaflet)
leaflet(sudamerica_table) %>% addTiles() %>%
		addCircleMarkers(lng=~longitude, lat=~latitude, color="red",
				opacity=0.3, radius=1)
```
