---
title: "News"
output:
  html_document:
    include:
      before_body: topbar_news.html
      after_body: footer.html
    css: styles_news.css
---

Any important news will be published in this area.
For comments or suggestions, use the
[issues](https://github.com/kamapu/kamapu.github.io/issues) site.

<br/>

<div style="background-color: #d2d3dc; text-align: left; padding: 10px;
border-radius: 15px">

# Package vegtable is on CRAN
*2017-08-08*

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/vegtable)](https://cran.r-project.org/package=vegtable)
[![total downloads](http://cranlogs.r-pkg.org/badges/grand-total/vegtable)](http://cranlogs.r-pkg.org/badges/grand-total/vegtable)

The package `vegtable` defines an object containing vegetation-plot data
sets and many functions for handling these data.
You can install it in your **R** session:

```{r install_vegtable_cran, eval=FALSE}
install.packages("vegtable", dependencies=TRUE)
```

To load the last version from **GitHub** you can still use:

```{r install_vegtable_github, eval=FALSE}
library(devtools)
install_github("kamapu/vegtable")
```

Examples of its applications are available at
[https://kamapu.github.io/workshops_freiburg_2017.html](https://kamapu.github.io/workshops_freiburg_2017.html).

</div>


<br/>

<div style="background-color: #deefbc; text-align: left; padding: 10px;
border-radius: 15px">

# Package taxlist launched in CRAN
*2017-06-14*

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/taxlist)](https://cran.r-project.org/package=taxlist)
[![total downloads](http://cranlogs.r-pkg.org/badges/grand-total/taxlist)](http://cranlogs.r-pkg.org/badges/grand-total/taxlist)

After a long time of conceptualization and development, `taxlist` is already
available at **CRAN**.
Thus you can install it in your **R** session:

```{r install_cran, eval=FALSE}
install.packages("taxlist", dependencies=TRUE)
```

To load the last version from **GitHub** you can still use:

```{r install_github, eval=FALSE}
library(devtools)
install_github("kamapu/taxlist", build_vignettes=TRUE)
```

Examples of its use will be published in
[Workshops](https://kamapu.github.io/workshops.html)

</div>

<br/>
