---
title: "Displaying taxonomic names in taxlist"
description: |
  Abstract about concepts and names.
author:
  - name: Miguel Alvarez
    url: https://kamapu.github.io/
date: 07-03-2021
output:
  distill::distill_article:
    self_contained: false
draft: true
categories:
  - R
  - taxonomy
preview: na
---

```{r setup, include=FALSE}
library(knitr)
library(biblio)

## Set global chunk options
opts_chunk$set(out.width="100%", echo=TRUE)

## # Chunk selecting references
## Bib <- read_bib("MiguelReferences.bib")
## Sel <- match_keys(Bib, "vegtablepress2.Rmd")$bibtexkey
## Bib2 <- subset(Bib, bibtexkey %in% Sel)
## biblio::write_bib(Bib2, file="press2refs.bib")
```

# Installation

Since some of the functions explained in this post are not available
in the current CRAN version of `taxlist`, you may need to install the package
from its **GitHub** repository.

```{r installation2, eval=FALSE}
library(devtools)
install_github("ropensci/taxlist", build_vignettes=TRUE)
```

# Revisiting taxlist

To recapitulate, an object of class `taxlist` contains four slots that
corresponds to four data frames.
From them the essentials are **taxonNames** collecting all taxon usage names,
and **taxonRelations**, which includes all taxon concepts, indicating their
taxonomic rank and the respective parent taxon.
While in slot **taxonNames** each usage name is already assigned to a taxon
concept, in slot **taxonRelations** it is indicated, which name is considered
the accepted name for the taxon.

**_here the data scheme_**

The slots **taxonViews** and **taxonTraits** can be considered as optional.
In **taxonViews** is the list of bibliographic references that define the
respective circumscriptions of the taxonomic concepts, while the slot
**taxonTraits** contains attributes of the concepts, for instance functional
traits for species, chorology, indicator values, life forms, etc.

# Accessing names and concepts

The main entries associated to a taxon concept are the concept itself (entries
in **taxonRelations**) and the respective usage names (entries in
**taxonNames**).
Their respective identifiers are called **TaxonConceptID** and **TaxonUsageID**.
Note that both IDs may be confounded because in some taxonomic concepts can be
identical but they can also be quite different.
Both identities are displayed when calling the function `summary()`.

```{r}
library(taxlist)
summary(Easplist, "papyrus")
```

**_Described summary output_**



Show the respective code in slot relations.

Respective code in slot names.

# Hierarchies


Summary of the object and mention to taxonomic ranks (levels).

When looking at the summary of a single taxon concept, both the taxonomic rank
and the parental taxon are also shown in the display, if existent.

Display of all information by summary.


Indented lists.



