---
title: "SWEA-Dataveg: A vegetation-plot database for Africa"
description: |
  A collection of vegetation-plots from Africa, originally focused on wetland
  vegetation from Eastern Africa, it is currently expanded to other areas
  and considering any kind of vegetation.
author:
  - name: Miguel Alvarez
    url: https://kamapu.github.io/
date: "`r format(Sys.time(), '%m-%d-%Y')`"
output:
  distill::distill_article:
    self_contained: false
draft: false
categories:
  - database
  - vegetation
# preview:
canonical_url: https://kamapu.github.io/sweadataveg
---

**Vegetation-plot data from Eastern Africa and abroad**

[![GIVD](badges/swea_givd.svg)](http://www.givd.info/ID/AF-00-006)
[![version](badges/sweadataveg_version.svg)](sweadataveg.html)

```{r import_swea, echo=FALSE, results="hide"}
# Object already exists in the session
#load("M:/WorkspaceR/00_Documents/update_databases/sweadataveg.rda")
```

The database **SWEA-Dataveg** is formatted in **PostgreSQL**, including the
extension **PostGIS**. For data exchange (after a respective agreement with the
custodian), objects of class
[**`vegtable`**](https://github.com/kamapu/vegtable) will be preferred.

**SWEA-Dataveg** contains currently records from
**`r format(nrow(swea), big.mark=",")`** plot observations that are
provided by
**`r format(length(unique(swea$data_source)), big.mark=",")`**
sources. Most of those sources are works published either as journal articles or
monographs.

The oldest record was done in
**`r format(min(swea$record_date, na.rm=TRUE), "%d-%m-%Y")`**, while
the newest record is from
**`r format(max(swea$record_date, na.rm=TRUE), "%d-%m-%Y")`**.

```{r map_sweadataveg, echo=FALSE, message=FALSE, out.width="100%"}
library(leaflet)
leaflet(swea) %>% addTiles() %>%
		addCircleMarkers(lng=~longitude, lat=~latitude, color="red",
				opacity=0.3, radius=1)
```
